\documentclass[a4paper,10pt]{moderncv}
\moderncvstyle{banking} % style options are 'classic', 'casual', 'modern', 'banking'
\moderncvcolor{blue} % color options are 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'
\usepackage[utf8]{inputenc}

% Personal data
\name{BABATUNDE}{OSHODI}
\address{3450 Roxboro Rd Ne}{Atlanta, GA}
\phone[mobile]{[678.462.7327]}
\email{[tundeoshodi99@gmail.com]}
\social[linkedin]{babatunde-oshodi-430689289}
\extrainfo{[Optional: Add any other contact details or links]}

\begin{document}

\makecvtitle

\section{Professional Summary}
Dedicated and results-driven Machine Learning Engineer with extensive experience in developing, implementing, and supporting machine learning algorithms and models. Proficient in Python, data engineering practices, and cloud technologies such as Google Cloud Platform. Adept at collaborating with cross-functional teams to create scalable and reliable ML solutions that meet business requirements. Passionate about continuous learning and applying cutting-edge techniques to solve complex problems. Ready to contribute to innovative product teams in a fast-paced, collaborative environment.

\section{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python (Preferred), SQL, JavaScript, HTML, CSS
    \item \textbf{Machine Learning \& AI Tools:} TensorFlow, PyTorch, Scikit-learn, SciPy, Pandas, Jupyter Notebooks, Gensim
    \item \textbf{Big Data Platforms:} BigQuery, Data Store
    \item \textbf{Cloud Platforms:} Google Cloud Platform (GCP), Vertex AI, BigQueryML, AutoML
    \item \textbf{Web Technologies:} ReactJS, Node.js, D3.js
    \item \textbf{Version Control:} Git
    \item \textbf{CI/CD Tools:} Jenkins, GitLab CI
    \item \textbf{Operating Systems:} Linux, Unix
    \item \textbf{Additional Skills:} SQL, REST APIs, Front-end Web Development, Data Analysis, Statistical Analysis, Anomaly Detection, Neural Networks
\end{itemize}


\section{Professional Experience}
\cventry{June 2023 -- Sept 2024}{Machine Learning Engineer II}{Blue Chip Technologies}{Westlands, Nairobi}{Hybrid - Contract}{
\begin{itemize}
\item Collaborated with product teams (UX, engineering, and product management) to design and implement secure, scalable machine learning solutions that meet business needs.
\item Designed and deployed AI/ML algorithms directly into software products to optimize performance and user experience.
\item Wrote custom code and scripts to automate infrastructure, monitoring services, and test cases.
\item Created dashboards, logging, and alerting systems to ensure proactive issue detection and resolution.
\item Contributed to code reviews, ensuring adherence to best practices and quality standards in the development of machine learning applications.
\item Participated in the full machine learning lifecycle, including data preprocessing, feature engineering, model training, and performance tuning.
\item Provided application support for software running in production and collaborated across teams to enable system scalability and efficiency.
\end{itemize}}

\cventry{Jan 2024 -- Present}{Machine Learning Engineer I}{Outlier.ai}{Remote}{Freelance}{
\begin{itemize}
\item Developed machine learning models for various applications, including clustering, forecasting, and anomaly detection.
\item Worked with cross-functional teams to implement machine learning solutions, improving system performance and operational efficiency.
\item Participated in creating production-level models using TensorFlow and Scikit-learn, which helped reduce errors and enhance customer experience.
\item Implemented best practices for model version control, testing, and performance monitoring.
\item Collaborated on designing and maintaining data pipelines and handling large datasets for analytics and predictive modeling.
\end{itemize}}

\section{Education}
\cventry{2004}{B.Sc. in Electrical and Electronics Engineering}{University of Lagos}{Lagos, Nigeria}{}{}

\section{Certifications}
\begin{itemize}
    \item \textbf{IBM AI Developer Professional Certificate}, [IBM, in progress]
    \item \textbf{Machine Learning with Python}
    \item \textbf{Google Cloud Professional Machine Learning Engineer}, [In Progress, Google]
    \item \textbf{Customer Service with Python: Build a Chatbot using ChatGPT}, Coursera Project Network
    \item \textbf{ChatGPT Prompt Engineering for Developers}, DeepLearning.AI
    \item \textbf{Pretraining LLMs}, DeepLearning.AI
    \item \textbf{Google AI Essentials}, Google
    \item \textbf{Foundations of Cybersecurity}, Google
    \item \textbf{Play It Safe: Manage Security Risks}, Google
\end{itemize}


\section{Projects}
\begin{itemize}
    \item \textbf{Offline Personal Assistant (Python/Django):} Developed an offline personal assistant capable of accessing files, scheduling tasks, and retrieving data. Ensured the assistant was lightweight, fast, and secure, offering a simple user interface without requiring online connectivity.
    \item \textbf{Property Management System (Django/Flask):} Built a property management system that allows property owners to track payments, due dates, and tenant records. Integrated authentication and client logins for managing and viewing property-related tasks securely.
\end{itemize}


\section{Professional Development}
\begin{itemize}
    \item Continuously engaging in self-paced learning activities (online tutorials, courses, webinars) to stay updated with the latest developments in ML and AI.
    \item Actively contributing to online communities and forums to share knowledge and solve complex technical problems.
    \item Actively working towards IBM AI Developer Professional Certification.
\end{itemize}

\section{Key Competencies}
\begin{itemize}
    \item \textbf{Collaboration:} Demonstrated ability to work with cross-functional teams (engineers, UX/UI designers, and product managers) to create and implement innovative machine learning solutions.
    \item \textbf{Adaptability:} Skilled at quickly learning new technologies and applying them to real-world challenges.
    \item \textbf{Problem Solving:} Focused on leveraging data and algorithms to provide actionable insights and efficient solutions.
    \item \textbf{Communication:} Able to present complex technical concepts in clear, user-friendly formats to diverse stakeholders.
\end{itemize}


\end{document}


